### 2018-01-15 master/paper.tex
Fix typo

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
    void start( [send(sNetworkAlloc),size_is(size)]int8_t *outputp, .., .. );
    void read( [receive(sNetworkAlloc),size_is(*size)]int8_t **inputp, .., .. );
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description of the nic driver (An example of send/receive)}
\label{src:SendReceive}
\end{figure}

@@

TINET+TECS supports legacy codes because TECS supports {\it Adapter} functionality, which enables to calling a function in TECS from existing C codes.
The adapter is implemented between C codes and a TECS component and links a C function to a TECS function as shown in Fig. \ref{fig:TECSAdapter}.
In TINET+TECS, when an application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls a function of tTCPCEP such as {\it eAPI\_sendData}.
Note that {\it tcp\_snd\_dat} is defined under the name {\it eAPI\_sendData} in TINET+TECS.
The adapter wraps the APIs used in the existing applications into TECS functions, enabling software developers to utilize an existing TCP/IP application via the adapter.

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tTLSFMalloc {
    [inline]entry  sMalloc  eMalloc;
    attr {
        size_t  memoryPoolSize;
    };
    var {
        [size_is(memoryPoolSize/8)]uint64_t *pool;
    };
};
\end{lstlisting}
\caption{Celltype description of TLSF memory allocator component}  
\label{src:TLSFCelltype}
\end{figure}

@@

Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
When the VM is activated, a large memory is allocated and the initialization is performed.
After that, the application is running and the VM is termnated.
The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
TLSF+TECS can visualize the behavior of GC and help to verify its operation.
Furthermore, when the VM is terminated, the memory used by VM is not completely released and a little used memory remains.
In this way, it is useful for finding bugs related to memory, which is hard to find.

@@

%Publication List
\chapter*{Publication List}
\addcontentsline{toc}{chapter}{Published List}
\section*{Journal}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
    ``Component-Based mruby Platform for IoT Devices,"
    \emph{IPSJ Journal of Information Processing},
    2017 (submitted).
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development,''
    \emph{JSSST Journal on Computer Software},
    vol. 34, no. 4, pp. 3-16, 2017.
\end{enumerate}

>>>>

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start([send(sNetworkAlloc),size_is(size)]int8_t *outputp, .., ..);
  void read([receive(sNetworkAlloc),size_is(*size)]int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description of the nic driver (An example of send/receive)}
\label{src:SendReceive}
\end{figure}

@@

TINET+TECS supports legacy codes because TECS supports {\it Adapter} functionality, which enables to call functions in TECS from existing C codes.
The adapter is implemented between C codes and a TECS component and links a C function to a TECS function as shown in Fig. \ref{fig:TECSAdapter}.
In TINET+TECS, when an application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls a function of tTCPCEP such as {\it eAPI\_sendData}.
Note that {\it tcp\_snd\_dat} is defined under the name {\it eAPI\_sendData} in TINET+TECS.
The adapter wraps the APIs used in the existing applications into TECS functions, enabling software developers to utilize an existing TCP/IP application via the adapter.

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tTLSFMalloc {
    [inline]
        entry  sMalloc  eMalloc;
    attr {
        size_t  memoryPoolSize;
    };
    var {
        [size_is(memoryPoolSize/8)]
            uint64_t *pool;
    };
};
\end{lstlisting}
\caption{Celltype description of TLSF memory allocator component}  
\label{src:TLSFCelltype}
\end{figure}

@@

Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
When the VM is activated, a large memory is allocated and the initialization is performed.
After that, the application is running and the VM is terminated.
The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
TLSF+TECS can visualize the behavior of GC and help to verify its operation.
Furthermore, when the VM is terminated, the memory used by VM is not completely released and a little used memory remains.
In this way, it is useful for finding bugs related to memory, which is hard to find.

@@

%Publication List
\chapter*{Publication List}
\addcontentsline{toc}{chapter}{Publication List}
\section*{Journal}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
    ``Component-Based mruby Platform for IoT Devices,"
    \emph{IPSJ Journal of Information Processing},
    2017 (submitted).
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development,''
    \emph{JSSST Journal on Computer Software},
    vol. 34, no. 4, pp. 3-16, 2017.
\end{enumerate}
